Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-24 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Results

% Anuncements
In order to start each of the experiments was promoted through social networks
particularly on the Facebook and Twitter platforms. The link used in the call for participation
was shortened URL, in order to obtain additional analytic data of the visitors.
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.

@@

% Time
\subsection{Results}
\label{sec:results}
Before launch, each deployment was first tried with a few beta testers. When applying the gammification
technique for the first time a problem was found in this beta stage. Some users were chating by 
giving a rating to an animation even before it was returned from the server, this was done by just
constantly pressing the mouse button. This is a common problem found in systmes appling leader boards.
By making the rewards for tasks achievements visible to other players or providing leader boards are ways of 
encouraging players to compete \cite{hickman2010total}. Because the  problematic consequences of competition, 
which can result in negative conduct, low cooperation and collaboration, or disadvantaging certain player
demographics such as women \cite{kumar2013gamification}, best-practice gamification designs try to
refrain from using this element. In order to measure the effect of the leader board in the system, the 
problem of cheating was mitigated by disabling the buttons for a certain amount of time. But the problem 
persists, competitive users will try to get in to the leader board by other means. 
% 
% Future work could compare the use of gamification with out leaderboards
%

@@

\begin{figure*}[!t]
    \centering
        \includegraphics[width=3.5in]{img/comparison.png}
    \caption{Top ranked number individuals rated by user using a
     logarithmic scale.}
    \label{fig:top-ranked-participation}
\end{figure*}

>>>>

% Anuncements
In order to start each of the experiments was promoted through social networks
particularly on the Facebook and Twitter platforms.
Is important to note that participants needed to log-in to facebook and give permissions to the application
in order to participate, there where no anonymous volunteers. 
The link used in the call for participation
was shortened URL, in order to obtain additional analytic data of the visitors.
In table \ref{tab:urls} the URL for each deployment in the Heroku platform is shown,
along with the short URL and the analytics link. In the same table a link to the GitHub 
application repository used to deploy to Heroku is also listed.

@@

% Time
\subsection{Results}
\label{sec:results}

Before launch, each deployment was first tried with a few beta testers. When applying the gammification
technique for the first time a problem was found in this beta stage. Some users were chating by 
giving a rating to an animation even before it was returned from the server, this was done by just
constantly pressing the mouse button. This is a common problem found in systmes appling leader boards.
By making the rewards for tasks achievements visible to other players or providing leader boards are ways of 
encouraging players to compete \cite{hickman2010total}. Because the  problematic consequences of competition, 
which can result in negative conduct, low cooperation and collaboration, or disadvantaging certain player
demographics such as women \cite{kumar2013gamification}, best-practice gamification designs try to
refrain from using this element. In order to measure the effect of the leader board in the system, the 
problem of cheating was mitigated by disabling the buttons for a certain amount of time. But the problem 
persists, competitive users will try to get in to the leader board by other means. 
% 
% Future work could compare the use of gamification with out leaderboards
%

@@

The results of each of the three experiments in terms of participation are detailed next.

\subsubsection{ Base deployment}
After a week of the anouncement the total number of volunteers for this experiment was 53 registered users. 
The total number of nodes generated in the graph was 595, with a total of 2220 relationships. In this
experiment a total of 500 new individuals where generated. The total number of evaluated
individuals for each volunteer is presented in figure \ref{fig:top-ranked-participation} with a blue line.

\subsubsection{ Non Graph Gamification deployment}
The total number of volunteers for this experiment was very close to those obtained in the previous
experiment: 54 registered users. The total number of nodes generated in the graph was 648, 
with a total of 2596 relationships. These numbers are close to those obtained in the base experiment,
with a marginal increase in participation. The increased participation also helped in the creation of
more individuals for a total of 648. The total number of evaluated
individuals for each volunteer is presented in figure \ref{fig:top-ranked-participation} with a red line.

\subsubsection{ Graph Gamification deployment}
This experiment had the higher number of volunteers for for a total of 68 registered users. 
In this experiment a total of 3594 new individuals where generated in the experiment. 
The total number of evaluated individuals for each volunteer is presented in figure 
\ref{fig:top-ranked-participation} in green.

\subsubsection{ Comparasion Results}
The results presented in figure \ref{fig:top-ranked-participation}, show that those users with
higher level of participation in deployments B and G, had about the same behavior, but the difference
came with users with medium level of participation, in this case participants where more engaged in deployment
G. When comparing all the experiments the deployment GG had the higher number of participation in users
of all levels.

\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Top ranked number individuals rated by user using a
     logarithmic scale.}
    \label{fig:top-ranked-participation}
\end{figure*}
